---
title: "POLS 204: Performing Research in Political Science"
format:
    html: default
    pdf: 
      documentclass: article
      fontsize: 12pt
      colorlinks: true
      citecolor: DarkViolet
      linkcolor: DarkViolet
      urlcolor: DarkViolet
      geometry: margin=1in
      output-file: "POLS204_syllabus"
---

```{r setup, message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(tibble)
library(pander)
```

::: {.content-visible when-format="pdf"}

\begin{center}

\vspace{-5em}

\url{ {{< var course.url >}} } \vspace{-1ex}

{{< var course.time >}} {{< var course.days >}} \vspace{-1ex}

{{< var course.location >}} \vspace{-1ex}

{{< var course.semester >}}

\end{center}


## Instructor

{{< var instructor.name >}} \vspace{-1ex}

Email: [{{< var instructor.email >}}](mailto:{{< var instructor.email >}}) \vspace{-1ex}

Office: {{< var instructor.office >}} \vspace{-1ex}

Office hours: [WF 1:00-3:00 pm]({{< var instructor.appointment_url >}}) and by appointment

:::


::: {.content-visible when-format="html"}

::: {.grid .course-details .course-details-smaller}

::: {.g-col-6}
### Course details

- {{< fa calendar >}} &nbsp; {{< var course.days >}}
- {{< fa calendar-alt >}} &nbsp; {{< var course.dates >}}
- {{< fa clock >}} &nbsp; {{< var course.time >}}
- {{< fa location-dot >}} &nbsp; {{< var course.location >}}
:::

::: {.g-col-6}
### Instructor

- {{< fa user >}} &nbsp; [{{< var instructor.name >}}]({{< var instructor.url >}})
- {{< fa university >}} &nbsp; {{< var instructor.office >}}
- {{< fa envelope >}} &nbsp; [{{< var instructor.email >}}](mailto:{{< var instructor.email >}})
- {{< fa university >}} &nbsp; Office hours: [WF 1:00-3:00 pm]({{< var instructor.appointment_url >}}) and by appointment
:::

:::



# Syllabus

You can download a PDF version of the syllabus with the weekly schedule here.
 
[<span class="btn btn-danger">{{< fa file-pdf >}} Syllabus </span></p>](POLS204_syllabus.pdf)



:::


## Course Overview

This course provides students with an introduction to quantitative and qualitative political science research that is necessary for original research on political and policy issues. The course focuses on three things: the development and analysis of political science research, the application of quantitative analysis, and an understanding of qualitative approaches such as interviewing and archival research. The course emphasizes hands-on training that will provide students useful skills for academic and professional setting, including an introduction to statistical software, measurement and introductory statistical analysis, the presentation of data, and strong writing. No prior data analysis or statistics background is necessary.


## Learning Outcomes

- Understand and assess empirical research in political science
- Estimate and interpret the appropriate quantities of interest to answer political science questions
- Develop and test research questions as well as communicating results from data analysis
- Understand and explain fundamental concepts of statistical inference and the advantages and limitations of quantitative methods


## Work and Assessment


### Required Materials:

- Llaudet, Elena and Kosuke Imai. 2022. [Data Analysis for Social Science: A Friendly and Practical Introduction](https://press.princeton.edu/books/paperback/9780691199436/data-analysis-for-social-science). United States: Princeton University Press. {{< fa book >}}
- A computer (Mac, Windows or Linux, preferably). If you are using a Chromebook or iPad, please let me know as soon as possible.
- Dropbox folder with readings and datasets {{< fa brands dropbox >}} (link on Canvas; please download)



### Course Expectations

Students are expected to attend class and participate in class discussions and exercises. I expected you will have completed all readings prior to class and will come prepared with questions.


### Course Workload

As a course with a course count of one, you are expected to spend 8-10 hours of work each week (not including our three 50-minute weekly course meetings).


### Assignments and grades

Final course grades will be assigned as follows:

```{r grades, include=FALSE}
grading <- tribble(
  ~Grade, ~Range, ~Grade1, ~Range1,
  "A",  "94–100%", "C",  "74–76%",
  "A−", "90–93%", "C−", "70–73%",
  "B+", "87–89%", "D+", "67–69%",
  "B",  "84–86%", "D",  "64–66%",
  "B−", "80–83%", "D−", "60–63%",
  "C+", "77–79%", "F",  "< 60%"
)
```

<div class="centered-table">

```{r show-grades-table, echo=FALSE, results="asis"}
grading %>%
  pandoc.table(justify = "lclc",
               col.names = c("Grade", "Range", "Grade", "Range"))
```

<div>


Final grades will be calculated based on the following components:

**Participation (10%)**: All students are expected to be active participants in the class. Our learning experience will be enhanced if you come prepared and ready to engage with the material and asks questions. If you are confused about something, you are likely not the only one.

  - <ins>*Attendance policy:*</ins> Attendance is part of your participation grade, and while there is no separate grade for attendance it is a prerequisite for in-class participation. That said, to accommodate unforeseeable circumstances, you have two *unexcused* absences that will not affect your participation grade. Any additional absences will hurt your participation grade. If you accumulate four *unexcused* absences in the semester, you will forfeit your entire participation grade. Note that students who are absent, whether excused or not, are still expected to submit the weekly summary corresponding to that class period. (Absences due to extenuating circumstances will be considered separately. Please refer to the [College's Class Attendance Policy](https://catalog.holycross.edu/requirements-policies/academic-policies/#coursepoliciestext-otp2) for the college-wide policy on absences and be in communication if a situation that will keep you from attending class for an extended period of time arises.)


**Problem Sets (30%)**: You will complete six (6) problem sets throughout the semester. These problem sets will help you practice the concepts and data analysis skills we learn in class. You will have about a week to complete each problem set. I encourage you to work together with other students, but the final product should be your own work. Problem sets are due at the beginning of the class period indicated on the schedule.


**Group Research Project (30% total)**: In research teams of two or three, you will write an empirical research paper (6-8 pages, double-spaced) similar to the ones political scientists publish in academic journals. For this assignment, you will use data from the American National Election Studies (ANES) to develop a research question, write a literature review, test a hypothesis, and report your results. The paper will be broken down into the following parts that you will submit throughout the semester:

  1. Research Question (5% of final grade)
  2. Literature Review and Expectations (2-3 pages, 5% of final grade)
  4. Conference-style Presentation (12-minutes, 10% of final grade)
  3. Final paper (6-8 pages, 10% of final grade)



**Midterm and Final Exam (15% each)**: The midterm and final exam will be similar in structure to the weekly problem sets. For these exams, you will be working with some popular survey data that social scientists collect with regularity, such as the General Social Survey and American National Election Study datasets. No collaboration is permitted for the exams. However, students are allowed to use a single letter-sized sheet of hand-written notes (two-sided). Both midterm and final exams will be administered via Canvas.

**Extra Credit Opportunity**: There is an additional problem set you can complete for extra credit. This can add a maximum of three (3) percentage points to your final grade.



## Collaboration Policy

Learning how to analyze data can be challenging but it may be easier if you work together. In fact, I encourage you to talk with your peers about the course materials and assignments. That said, each student should do and submit their own work. Collaboration does not mean you end up with the exact same code or answer.


## Communication Policy

If you have questions about class in general or about a specific assignment, you can email me or come by my office. You can expect a response within 24 hours (unless you email me on Friday). Students are also more than welcome to attend office hours, as this is time set aside specifically for you. In addition, if my office door is open, feel free to stop by. Please note that I will not be "pre-grading" assignments, but I am happy to answer clarifying questions about them either via email or, preferably, during office hours.


## Regrading Policy

If a student wishes to appeal a grade, they must do so in writing within one week of receiving their graded assignment back. The student must indicate clearly what part of the assignment's grading they disagree with, making sure to respond to the instructor's comments in that section and making their case for why they should not have been deducted points. These requests should be done via email and the subject name should read "POLS 204 Regrading request - [Name of assignment]." 


## Academic Integrity and Generative AI Policy

All education is a cooperative enterprise between faculty and students. This cooperation requires trust and mutual respect, which are only possible in an environment governed by the principles of academic integrity. As an institution devoted to teaching, learning, and intellectual inquiry, Holy Cross expects all members of the College community to abide by the highest standards of academic integrity. Any violation of academic integrity undermines the student-faculty relationship, thereby wounding the whole community. Students in this class are required to read the full text of the [College’s Academic Integrity Policy](https://catalog.holycross.edu/requirements-policies/academic-policies/#academicintegritytext) and to abide by its standards.

Unless otherwise noted, you are expected to complete all coursework independently without the use of generative AI tools (e.g., ChatGPT, Claude, Gemini). Because this course emphasizes learning basic programming skills, using AI tools at this stage runs counter to our goals. Because the assumption in this course is that all code students submit is original to them, cases where students turn in AI-generated content will be considered cheating.

Instead of relying on AI tools, I encourage you to use forums like Stack Overflow. If you are unsure about how make your code do what you want or do not know how to fix code that won't run, chances are someone has asked a similar question in Stack Overflow and you can repurpose the code people share there. 




## Course Accessibility and Academic Accommodations


The College of the Holy Cross is committed ["to providing students with disabilities equal access to the educational opportunities and programs available at Holy Cross in accordance with the Americans with Disabilities Act of 1990 as amended, Section 504 of the Rehabilitation Act of 1973, and Massachusetts laws."](https://catalog.holycross.edu/requirements-policies/academic-policies/#coursepoliciestext)

Any student who feels the need for accommodation based on the impact of a disability should contact the [Office of Accessibility Services](https://www.holycross.edu/community/health-wellness/accessibility-accommodations) to discuss support services available. Once the office receives documentation supporting the request for accommodation, the student would meet privately with Accessibility Services to discuss reasonable and appropriate accommodations.

The office can be reached by calling 508-793-3693. If you are already registered with Accessibility Services, please be sure to get your accommodation letters and deliver them to your instructors in a timely fashion. Instructors need at least 4-5 days advance notice to be able to facilitate the process of receiving testing accommodations.



## Wellbeing and Mental Health

The wellbeing and mental health of students is important. If you are having trouble managing your coursework and are experiencing unusual amounts of stress, sadness, or anxiety, the College has resources you may find useful. Please reach out to [Student Wellness Education](https://www.holycross.edu/community/health-wellness/student-wellness-education) or the office of [Counseling and Psychological Services](https://www.holycross.edu/community/health-wellness/counseling-psychological-services).


## Title IX

If you have experienced any form of sexual harassment or violence, dating or domestic violence, or stalking, please talk to any faculty or staff member with whom you feel comfortable. Faculty and staff members want to support you and have been trained to help. They will also inform the Title IX office so that you learn about options available to you. If you do not want college administrators to know what you have experienced, you may speak to a chaplain or counseling services with complete confidentiality. They will not tell anyone what you share with them unless you give your express permission. You may contact the Title IX Office directly at <titleix@holycross.edu>.


## Chosen Names and Personal Pronouns
 
Everyone has the right to be addressed by the name and pronouns that correspond to their gender identity. Rosters do not list gender or pronouns, so you may indicate the pronouns you use so that I don't make assumptions based on your name and/or appearance/self-presentation. If you use a chosen name, please let me know. Chosen names and pronouns are to be respected at all times in the classroom. Mistakes in addressing one another may happen, so I encourage an environment of openness to correction and learning. I will not however, tolerate repeated comments which disrespect or antagonize students who have indicated pronouns or a chosen name.


## Center for Writing and Writer's Workshop

The Center for Writing offers one-on-one appointments with trained peer consultants trough their Writer's Workshop who can help you improve your communication skills. You are encouraged to use this resource when working on your class assignments to make your arguments more compelling, your sentences clearer, and persistent grammatical errors nonexistent. You can schedule an appointment at <https://holycross.mywconline.com/>.



## Recording of Classes

Please note that, consistent with applicable federal and state law, this course may be video/audio recorded as an accommodation *only* with permission from the Office of Accessibility Services. Students are not permitted to record the contents of this class under any other circumstances.



## Syllabus Change Policy

This syllabus is only a guide for the course and is subject to change with advanced notice.


::: {.content-visible when-format="pdf"}
  
## Schedule

{{< include content/01-week1.qmd >}}

{{< include content/02-week2.qmd >}}

{{< include content/03-week3.qmd >}}

{{< include content/04-week4.qmd >}}

{{< include content/05-week5.qmd >}}

{{< include content/06-week6.qmd >}}

{{< include content/07-week7.qmd >}}

{{< include content/08-week8.qmd >}}

{{< include content/09-week9.qmd >}}

{{< include content/10-week10.qmd >}}

{{< include content/11-week11.qmd >}}

{{< include content/12-week12.qmd >}}

{{< include content/13-week13.qmd >}}

{{< include content/14-week14.qmd >}}

{{< include content/15-week15.qmd >}}

{{< include content/16-week16.qmd >}}

{{< include content/17-week17.qmd >}}

:::

{{< include index_title.qmd >}}
